---
title: "Sample creation vignette for using the PBMC dataset"
author: "RICHARD"
date: "2024-03-17"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This document provides an analysis of the **PBMC dataset** using `Seurat` package in R. We'll go through loading the dataset, initializing the `Seurat` object, performing quality control (QC) and visualization.

```{r libraries, message=FALSE, warning=FALSE}
library(dplyr)
library(Seurat)
library(patchwork)
```

## Load the PBMC Dataset

```{r dataset}
pbmc.data <- Read10X(data.dir = "C:\\Users\\richa\\Downloads\\filtered_gene_bc_matrices\\hg19")
knitr::kable(head(pbmc.data))
```

## Initialize the Seurat Object with the raw data (non-normalized data)

```{r object initialisation, warning=FALSE}
pbmc <- CreateSeuratObject(counts = pbmc.data, project = "pbmc3k", min.cells = 3, min.features = 200)

```

## Add QC Metrics to Metadata

``` {r qc metrics}
pbmc[["percent.mt"]] <- PercentageFeatureSet(pbmc, pattern = "^MT-")
```

## Visualize QC Metrics

```{r visualisation, warning=FALSE}
VlnPlot(pbmc, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), ncol = 3)
```

## Feature-Feature Relationships

```{r relationship}
plot1 <- FeatureScatter(pbmc, feature1 = "nCount_RNA", feature2 = "percent.mt")
plot2 <- FeatureScatter(pbmc, feature1 = "nCount_RNA", feature2 = "nFeature_RNA")
plot1 + plot2
```

## Conclusion

This document presented an analysis of the **PBMC dataset** using `Seurat` in R, including data loading, initialization of Seurat object, QC analysis, and visualization of feature-feature relationships.
